---
title: "HW5"
output: html_document
date: '2022-05-15'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(tidymodels)
library(ggplot2)
library(visdat)
library(corrplot)
library(discrim)
library(klaR)
library(yardstick)
library(glmnet)
set.seed(45)
```

```{r}
data <- read.csv('data/pokemon.csv')
head(data)
```

## Question 1

```{r}
library(janitor)
```

```{r}
data <- clean_names(data)
head(data)
```

The function changed all the capital letters included in the names of labels in the data into lower case letters. THis makes it much easier to handel the data since R is sensitive to lower case and lower case.

## Question 2

```{r}
data %>% ggplot(aes(x = type_1)) + 
  geom_bar()
```

According to bar plot, there are some types with very few pokemons, for example 'Flying' type.

```{r}
data <- filter(data, type_1 %in% c('Bug', 'Fire', 'Grass', 'Normal', 'Water', 'Psychic'))
head(data)
```

```{r}
data$type_1 = factor(data$type_1)
data$legendary = factor(data$legendary)
```

## Question 3

```{r}
data_split <- initial_split(data, prop = 0.8,
                                strata = type_1)
data_train <- training(data_split)
data_test <- testing(data_split)

cv_folds <- vfold_cv(data_train, v = 5, strata = type_1)
```

## Question 4

```{r}
pokemon_recipe = recipe(type_1 ~ legendary + generation + sp_atk, + attack + speed + defense + hp + sp_def, 
                        data = data_train) %>%
  step_dummy(c("legendary", "generation")) %>%
  step_dummy(generation) %>%
  step_center(all_predictors()) %>%
  step_scale(all_predictors())
  
```

## Question 5

```{r}
ela_mod = multinom_reg(penalty = tune(), mixture = tune()) %>%
  set_engine('glmnet') 

ela_work = workflow() %>%
  add_model(ela_mod) %>%
  add_recipe(pokemon_recipe)

ela_grid = grid_regular(penalty(range = c(-5, 5)), 
                      mixture(range = c(0, 1)), levels = 10)
```

5 cv folds, 10 mixture levels, and 10 penalty times make the total number of models 5 \* 10 \* 10 = 500.

## Question 6

```{r}
ela_res <- tune_grid(object = ela_work, resamples = cv_folds, grid = ela_grid)
```

```{r}
autoplot(ela_res)
```

## Question 7

```{r}
best_fit = ela_tune %>%
  select_best("roc_auc")

fit_final = ela_work %>%
  finalize_workflow(best_fit)

pokemon_fit = fit_final %>%
  fit(data_train)

pokemon_predict = augment(pokemon_fit, data_test)

```

## Question 8

```{r}
test_roc_auc = roc_auc(data = pokemon_predict, 
                       truth = type_1, 
                       estimate = c(.pred_Bug, .pred_Fire, .pred_Grass, 
                                  .pred_Normal, .pred_Psychic, .pred_Water), 
                       estimator = 'macro_weighted')
test_roc_auc$.estimate

test_curves = roc_curve(data = pokemon_predict, 
                        truth = type_1, 
                        estimate = c(.pred_Bug, .pred_Fire, .pred_Grass, 
                                    .pred_Normal, .pred_Psychic, .pred_Water))
autoplot(test_curves)

con_matrix = conf_mat(data = pokemon_predict, truth = type_1, estimate = .pred_class)
heatmap(con_matrix$table)

output: html_document
date: '2022-05-15'
---

knitr::opts_chunk$set(echo = TRUE)
```
